Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
minor

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
To estimate this the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach. It gives use an estimated $\alpha$ parameter that are summarized in the table~\ref{tab:mualpha}.

>>>>

Within this method we fist fit a power law to the data of one simulation by estimating the parameters of the power law equation $P(v)=C/v^\alpha $.
To estimate this, the method uses maximum likelihood estimator and Kolmogorof-Smirnov approach that gives use an estimated $\alpha$. The means of the $\alpha$ estimated for all our simulation are summarized in the table~\ref{tab:mualpha}.
